SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-05-17 scipy-1.0/ckdtree.tex

The \texttt{cKDTree} module, which implements a space-partitioning data structure that
organizes points in $k$-dimensional space, was rewritten in C++ with templated classes. 
Support was added for periodic boundary conditions, which are often used 
in simulations of physical processes.

>>>>

The \texttt{scipy.spatial.ckdtree} module, which implements a space-partitioning data structure that
organizes points in $k$-dimensional space, was rewritten in C++ with templated classes. 
Support was added for periodic boundary conditions, which are often used 
in simulations of physical processes.
